### 2014-10-15 PrivacyProtection-2014-09-09.tex
started summary fried

Defining privacy is a challenge which seems impossible. This is well put to words by Serge Gutwirth, who notes in \cite{Gutwirth}:

\begin{quote}
The notion of privacy remains out of the grasp of every academic chasing it. Even when it is cornered by such additional modifiers as `our' privacy, it still finds a way to remain elusive.
\end{quote}

Many privacy researchers seem to ``focus on the ways in which privacy can be infringed'' \cite{1}.
Thus they try to create taxonomies of \emph{privacy harms} instead of taxonomies of \emph{privacy types}.
Those two differ in the respect that the former focuses on threats to prohibit whereas the latter focuses on values to protect.
So one should rather evaluate what aspects are precious about privacy and develop measures to ensure their security than only forbid single actions against privacy \cite{1}.

>>>>

Defining privacy is a challenge which seems impossible. This is well put to words by Serge Gutwirth, who notes:

\begin{quote}
The notion of privacy remains out of the grasp of every academic chasing it. Even when it is cornered by such additional modifiers as `our' privacy, it still finds a way to remain elusive. \cite{Gutwirth}
\end{quote}

%Many researchers seem to only ``focus on the ways in which privacy can be infringed'' \cite{7ToP}.
%Thus they try to create taxonomies of \emph{privacy harms} instead of taxonomies of \emph{privacy types}.
%Those two differ in the respect that the former focuses on threats to prohibit whereas the latter focuses on values to protect.
%So one should rather evaluate what aspects are precious about privacy and develop measures to ensure their security than only forbid single actions against it \cite{7ToP}.

Many researchers seem to only ``focus on the ways in which privacy can be infringed'' \cite{7ToP}.
Thus they invest a great amount of work in defining threats to prohibit instead of describing why privacy is so valuable to us.
This way around one could derive measures to ensure and secure its value \cite{7ToP}.
One particular scholar who does this in the context of digital monitoring is Charles Fried.
He questioned, why we are so sensitive to violations of privacy.
But he did not assert privacy as an intrinsic value by itself, he rather sated:

\begin{quote}
Privacy is not simply an absence of information about us in the minds of others;
rather it is \textbf{the control we have over information about ourselves}. \cite{CFried:Privacy}
\end{quote}

According to Fried privacy is a \textit{rational context}.
Which means that one is aware of such context's existence during a rational action.
If we are to share private information with others, we are most likely aware that this action is privacy related.
In that case we are able to selectively disclose information along the two dimensions of quantity and quality.
This leads Fried to his thesis, that privacy is one's ability to create and modulate his or hers social relationships, namely: friendship, love and trust. \cite{CFried:Privacy}

Depending on the conversation partner, we change the degree of intimate information we share if it is a total stranger, colleague, close friend or lover.
With close friends or lovers we share information of great intimacy we do not share with anyone else.
Moreover, we trust those friends or lovers to not reveal information about us to others by respecting their privacy.
Trust needs the possibility of unknown failure.
If we would constantly monitor our partners, they cannot fail unnoticed nor can they willingly share that information with us.
Thus they could not trust us anymore. \cite{CFried:Privacy}

So privacy or the its possibility, according to Fried, is the foundation of our core relations: friendship, love and trust.
And thus it is valuable, because those relations are essential to human society \cite{CFried:Privacy}. 
Using his anatomy of privacy as foundation of our analysis is suitable because of two points.
At first, Fried's study on the understanding of privacy provided a great contribution to the research on the same term in philosophy \cite{sep-privacy} and computer science \cite{SociotechnicalArchitectureForOnlinePrivacy}.
Secondly, despite the fact his text was published in 1970, he already included technologies to its viewpoint that did not only monitor location, but also record biometric data.
